---
title: "Summary of Findings "
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(here)
```

## Comparison of the Padres' 2019 Season with their best hitter injured and uninjured

### Histogram of the Padres' 2019 Season with their best hitter injured and taken out of the latter games
```{r }
seasonsim <- read_csv(here("data","seasonsim.csv"))

ggplot()+
  geom_histogram(aes(x = seasonsim$season), fill = "sienna4", color = "yellow") +
  xlab("Wins in a Season (Fernando Tatis Jr. replaced after injury)") +
  ggtitle("Simulation of the Padres 2019 Season", 
          subtitle = "Dashed Line at the Padres Actual Number of 2019 Wins of 70") + 
  geom_vline(xintercept = 70, col = "navyblue", size = 1.5, linetype = "dashed")

```

The Padres won 70 games in the 2019 season. We simulated 250 seasons and found an average of `r mean(seasonsim$season)` games won per season. Fernando Tatis Jr. was injured during the season and was replaced in the line-up. 

Tatis Jr. is the Padres' best hitter and we wanted to know, if he hadn't been injured, would the Padres have made it to the playoffs?

### Histogram of the Padres' 2019 Season with their best hitter able to play all 162 games

```{r}
seasonsim_FTJ <- read_csv(here("data","seasonsim_FTJ.csv"))

ggplot()+
  geom_histogram(aes(x = seasonsim_FTJ$season), fill = "navyblue", color = "burlywood1") +
  xlab("Wins in a Season (Fernando Tatis Jr. played entire season)") +
  ggtitle("Simulation of the Padres 2019 Season with Fernando Tatis Jr.")
```

In order to get into the playoffs, a team needed 90 wins. Our simulation finds if Fernando Tatis Jr. had not been injured, the Padres' would have won an average `r mean(seasonsim_FTJ$season)` games. It seems that even if their best hitter had not been injuired, they would not have made it to the playoffs in 2019. 


